An Analysis of the Security Blind Spots of Software Composition Analysis caused By Cloning and Shading

### 2023-04-29 paper/evaluation.tex
worked on threats to validity section

\begin{table}
	\begin{tabular}{|p{4.5cm}p{2cm}p{3.5cm}|}
		\hline
		artifact (gav) & short name & description  \\ 
		\hline
		commons-collections:\-commons-collections:\-3.2.1 & collect & data structure library  \\
		com.alibaba:\-fastjson:\-1.2.80 & fast-json & JSON parser  \\
		org.yaml:\-snakeyaml:\-1.250 & snakeyaml & YAML parser \\
		org.apache.logging.\-log4j:\-log4j-core:\-2.14.1 & log4j & logging   \\
		\hline

		\hline
	\end{tabular}
	\caption{\label{tab:artifacts}Artifacts used in evaluation}
\end{table}

\begin{table}
	\begin{tabular}{|p{3cm}p{2cm}p{2.4cm}p{2.2cm}|}
		\hline
		CVE & artifact & CWEs  & severity  \\ 
		\hline
		CVE-2015-7501 & collect &  502  &  9.8 critical \\
	    CVE-2022-25845 & fastjson  & 502  & 9.8  critical \\
		CVE-2022-38749 & snakeyaml & 121, 787  &  6.5 medium \\
		CVE-2021-44228 & log4j & 20, 400, 502, 17 & 10  critical \\
		\hline

>>>>

\begin{table}
	\begin{tabular}{|p{4.5cm}p{2cm}p{3.5cm}|}
		\hline
		artifact (gav) & short name & description  \\ 
		\hline
		commons-collections:\-commons-collections:\-3.2.1 & collect & data structure library  \\
		com.alibaba:\-fastjson:\-1.2.80 & fast-json & JSON parser  \\
		org.yaml:\-snakeyaml:\-1.250 & snakeyaml & YAML parser \\
		org.apache.logging.\-log4j:\-log4j-core:\-2.14.1 & log4j & logging   \\
		org.apache-extras.beanshell.\-bsh.\-2.0b5 & beanshell & scripting DSL \\ 
		com.google.guava:\-guava:\-11.0.1 & guava & utilities and data structures \\
		org.apache.commons:\-commons-text:\-1.9 & c-text & string utilities \\
		\hline
	\end{tabular}
	\caption{\label{tab:artifacts}Artifacts used in evaluation}
\end{table}

\begin{table}
	\begin{tabular}{|p{3cm}p{2cm}p{2.4cm}p{2.2cm}|}
		\hline
		CVE & artifact & CWEs  & severity  \\ 
		\hline
		CVE-2015-7501 & collect &  502  &  9.8 critical \\
		CVE-2016-2510 & beanshell & 19 & 8.1 high \\ 
		CVE-2018-10237  & guava & 770 & 5.9 medium  \\
	    CVE-2022-25845 & fastjson  & 502  & 9.8  critical \\
		CVE-2022-38749 & snakeyaml & 121, 787  &  6.5 medium \\
		CVE-2021-44228 & log4j & 20, 400, 502, 17 & 10  critical \\
		CVE-2022-42889 & c-text & 94 & 9.8 critical \\ 
		\hline

### 2023-04-29 paper/threats.tex
worked on threats to validity section

The analysis is designed to be precise. This is ensured by making vulnerabilities testable. However, there is a possibility that those tests do not correctly reflect the vulnerability. While sometimes vulnerabilities are reported in great details (for instance, using parser payloads discovered by a fuzzer such as TODO), often reports are vague (and sometimes this is on purpose as part of the disclosure process), and proof-of-concepts are constructed from the understanding of an individual programmer of the vulnerability. However, sometimes those proof-of-concept projects becomes part of the definition of the vulnerability. We therefore think that the possibility of this introducing false positives into our analysis are low.

>>>>

The analysis is designed to be precise. This is ensured by making vulnerabilities testable. However, there is a possibility that those tests do not correctly reflect the vulnerability. While sometimes vulnerabilities are reported in great details (for instance, using parser payloads discovered by a fuzzer such as TODO), often reports are vague (and sometimes this is on purpose as part of the disclosure process), and proof-of-concepts are constructed from the understanding of an individual programmer of the vulnerability. Sometimes, those tests may miss some additional security measures clones may introduce - for instance, the tests for CVE-2022-42889 in commons-text-1.9 check whether interpolator lookups by default provide entries for the \textit{script}, \textit{dns} and \textit{url} prefixes, and test the execution of an OS command using the script prefix. Tests do not check whether actual network lookups happen with string prefixed dns and url. This is an engineering compromise -- additional network connectivity makes tests flaky , and slows down the pipeline, and we deem the overall risk that this introduces false positives very low.
